### 2024-03-25 doc/sections/introduction.tex
Add virginialake, Ozan cite,
Add Nguyễn and Straßburger

\begin{itemize}
      \item BV by Guglielmi~\cite{Guglielmi07:sis} is an extension of MLL inspired by process algebras such as CCS~\cite{Milner89:CC,Milner80:CCS} and Pomset Logic~\cite{Retore97:pomset}.
      \item MAV by Hornes~\cite{Horne15:mav} extends BV with the additives.
      \item BV adds a non-commutative connective to MLL. Such a connective can be motivated by coherence spaces, or by session types.
      \item A shallow sequent calculus cannot capture BV~\cite{Tiu06:sisii}.
      \item To make sure that a proof system makes sense, we need some kind
            of Cut-elimination theorem that ensures that all proofs can be
            placed into a normal form where it is evident that it is not
            possible to derive all results.
\end{itemize}

>>>>

We present an algebraic semantics and semantic proof of cut elimination for the multiplicative-additive deep inference calculus MAV~\cite{Horne15:mav}, an extension of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll} with a self-dual non-commutative connective.

Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems which arose from Guglielmi's attempts to relate process algebras~\cite[CCS]{Milner89:CC,Milner80:CCS} to linear logic~\cite{Girard87:ll}.
The problem is that, while the connectives of linear logic capture parallel composition, no connective captures \emph{sequential composition}.
Eventually, Guglielmi's attempts yielded the basic deep inference calculus, BV~\cite{Guglielmi99:bv,Guglielmi07:sis}, which extends multiplicative linear logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that does capture sequential composition.
Such a connective was already present in Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence spaces~\cite[Chapter 8]{GirardTL89:proofs}, which are a semantics for proofs of linear logic.
While BV is similar to Pomset logic, the two are not the same. Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that the theorems of BV are a proper subset of the theorems of Pomset logic.

% Neither BV nor Pomset logic has a sequent calculus.
% ~\cite{Tiu06:sisii}

\begin{itemize}
      \item BV~\cite{Guglielmi07:sis} by Guglielmi is an extension of MLL inspired by process algebras such as CCSand Pomset Logic~\cite{Retore97:pomset}.
      \item MAV by Hornes~\cite{Horne15:mav} extends BV with the additives.
      \item BV adds a non-commutative connective to MLL. Such a connective can be motivated by coherence spaces, or by session types.
      \item A shallow sequent calculus cannot capture BV~\cite{Tiu06:sisii}.
      \item To make sure that a proof system makes sense, we need some kind
            of Cut-elimination theorem that ensures that all proofs can be
            placed into a normal form where it is evident that it is not
            possible to derive all results.
\end{itemize}
